Sketch Recognition and Understanding

### 2009-09-26 trunk/draft/System.tex

	\includegraphics[scale=0.5]{afterDefense/clockstroke1.eps}
  &   &    \includegraphics[scale=0.5]{afterDefense/stroke1withpdp.jpg.eps}
\\ \hline 
Segmentation & Segmentation of Ellipse & $P_{dp}$   &  Ellipse fitting  & 
The circle is   a = 103.05715108084719 ,b = 103.06851874747797 , Center( 283.03365107691775,  181.05035287667172 )   with Error =  1.9471676673301757 , Percent =1.0695193086531243
eff  = 0.27463462099275116

@@

Stroke 2 & Extracting point and computing boundary data & -- &  see Section \ref{sec:Preprocessing} &
 	\includegraphics[scale=0.5]{afterDefense/clockstroke2.jpg.eps} \\ \hline
  & Possible Dominate point Extraction for details see Section\ref{sec:Preprocessing} &   	\includegraphics[scale=0.5]{afterDefense/clockstroke2.jpg.eps}  & 1. compute the $P_{pd}$  &

  \includegraphics[scale=0.5]{afterDefense/stroke2WithPdp.jpg.eps}
    \\ \hline

>>>>

%	\includegraphics[scale=0.5]{afterDefense/clockstroke1.eps}
  &   &    \includegraphics[scale=0.5]{afterDefense/stroke1withpdp.jpg.eps}
\\ \hline 
Segmentation & Segmentation of Ellipse & $P_{dp}$   &  Ellipse fitting  & 
The circle is   a = 103.05715108084719 ,b = 103.06851874747797 , Center( 283.03365107691775,  181.05035287667172 )   with Error =  1.9471676673301757 , Percent =1.0695193086531243
eff  = 0.27463462099275116

@@

Stroke 2 & Extracting point and computing boundary data & -- &  see Section \ref{sec:Preprocessing} &
 	\includegraphics[scale=0.5]{afterDefense/clockstroke2.jpg.eps} \\ \hline
  & Possible Dominate point Extraction for details see Section\ref{sec:Preprocessing} &   	%\includegraphics[scale=0.5]{afterDefense/clockstroke2.jpg.eps}
    & 1. compute the $P_{pd}$  &  
  \includegraphics[scale=0.5]{afterDefense/stroke2WithPdp.jpg.eps}
    \\ \hline
